\bf Estimating the number of clusters using cross-validation

### 2016-06-20 cvclust.tex
minor updates to jasa template

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{float}
%\usepackage{footnote}
%\usepackage[bottom]{footmisc}
\usepackage[singlelinecheck=false]{caption}

\usepackage{graphicx,psfrag,epsf}
\usepackage[space]{grffile}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL

%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{1}

@@

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{claim}{Claim}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}

@@

% convergence
\newcommand{\toas}{\overset{\mathit{a.s.}}{\to}}

\newcommand{\Oh}{O}
\newcommand{\OhP}{O_p}

@@

%\bibliographystyle{natbib}

@@

\if1\blind
{
  \title{\bf Estimating the number of clusters using cross-validation}
  \author{Wei Fu and Patrick O.\ Perry \\
  Stern School of Business, New York University}
  \maketitle
} \fi

\if0\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Estimating the number of clusters using cross-validation}
\end{center}
  \medskip
} \fi

@@

\noindent%
{\it Keywords:} clustering, cross-validation, $k$-means, model selection, unsupervised learning
\vfill

@@

\bibliographystyle{apalike}

\bibliography{references}
\end{document}

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage[singlelinecheck=false]{caption}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{float}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{url}

%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

@@

\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}

@@

% convergence
\newcommand{\toas}{\overset{\mathit{a.s.}}{\to}}
\newcommand{\Oh}{O}
\newcommand{\OhP}{O_p}

@@

@@

\if0\blind
{
  \title{\bf Estimating the number of clusters using cross-validation}
  \author{Wei Fu and Patrick O.\ Perry \hspace{.2cm} \\
  Stern School of Business, New York University}
  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Estimating the number of clusters using cross-validation}
\end{center}
  \medskip
} \fi

@@

\noindent%
{\it Keywords:} clustering, $k$-means, model selection, unsupervised learning
\vfill

@@

\bibliographystyle{apalike}
\bibliography{references}

\end{document}
